
---
title: "Spatial Analyses of wild boars data regarding on psycological patterns"
subtitle: "Semester Project for Patterns & Trends in Environmental Data FS22"
author: "Authors: Jonas Michael Windisch and Johannes Quente"
date: "Submission Date: 03.07.2022"
output:
  html_document:
    theme: journal
    highlight: tango
    toc: true
    toc_float: true
    code_download: true
    output_dir: "docs"
    code_folding: show

---


<style>
body {
text-align: justify;font-size: 17spx; line-height: 1.75em}
  }
</style>

<style>
#TOC {
  background: url("https://sges.ch/wp-content/uploads/2018/07/zhaw-iunr-logo.png");
  background-size: contain;
  padding-top: 250px !important;
  background-repeat: no-repeat;
}
</style>

## Abstract

xxx


## Introduction


In recent decades, an expansion and increase of wild boar (*Sus scrofa*) populations has been observed across Europe, with colonising agricultural and urban areas, thus increasing problems of cohabitation with humans (Rutten et al., 2020). In particular, the wild boar often comes into conflict with humans, the main problems being the transmission of diseases to domestic animals and humans, collisions with vehicles, disturbance or threat to citizens and damage to gardens, public parks, pasture and agriculture (Meng et al. 2009).

Wild boar damage to croplands is expressed in different ways: direct consumption of crops, rooting in search of bulbs, invertebrates or tubers, seed removal, trampling and damage to agricultural infrastructure (Barrios-García & Ballari 2012). Therefore, it is important to know their activity patterns and where and when the wild boars are in order to take countermeasures.

The research question been asked is: How can the different environments (settlements, streets and different land use categories) been contextualized with the activity-patterns of the wild boars. How can this be conceptualized, modeled and further implemented in suitable visualizations to show behavioral patterns given to a certain environmental context and help to answer questions like “What does wild boar fear?” or “What are the behavioral constraints of wild boars?”.


## Material and Methods

### Loading Libraries:

library(devtools)
library(ComputationalMovementAnalysisData)
library(ggplot2)
library(readr)
library(dplyr)
library(terra)
library(sf)
library(tmap)
library(SimilarityMeasures)
library(lubridate)
library(tidyr)
library(knitr)


### Data Aquision and Preprosessing
```{r message = FALSE, warning = FALSE , results = FALSE, fig.show = 'hide'}

install_github("ComputationalMovementAnalysis/ComputationalMovementAnalysisData")

```

### Analysing the data and its structure

```{r message = FALSE, warning = FALSE , results = FALSE, fig.show = 'hide'}
head(wildschwein_BE)
head(wildschwein_metadata)
head(wildschwein_overlap_temp)


write.csv(wildschwein_BE, file = "wildschwein_BE.csv")
write.csv(wildschwein_metadata, file = "wildschwein_metadata.csv")
write.csv(wildschwein_overlap_temp, file = "wildschwein_overlap_temp.csv")

```
### Filter to the newyear-period of 2014-2015

The Idea was to reduce the amount of data down to 7 wildboars and the timeperiod from the 2014-12-15 until the 2015-01-15. The result therefore is rather a simplified way to solve our question but  includes all the necessary means to answer this kind of question in a rather exemplary way. 
```{r message = FALSE, warning=FALSE}

ws_be_sf %>% 
  filter(DatetimeUTC >= as.Date("2014-12-15") & DatetimeUTC < as.Date("2015-01-15")) -> ws_newyear

```


### Deriving Speed in order to derive a proxy of the most active or laziest wildboar
```{r message = FALSE, warning = FALSE, results='hide', fig.show = TRUE}

ws_newyear <- ws_newyear %>%
  mutate(timelag = as.numeric(difftime(lead(DatetimeUTC),DatetimeUTC,units = "mins")))


ws_newyear_steplength <- ws_newyear %>%
  group_by(TierName) %>%
  mutate(
    steplength = sqrt((E-lead(E))^2+(N-lead(N))^2)
  )


ws_newyear_speed <- ws_newyear_steplength %>%
  group_by(TierName) %>%
  mutate(
    speed = steplength/timelag
  )

```


 
### Deriving another proxy: net displacent
```{r message = FALSE, warning = FALSE, results='hide', fig.show = TRUE}
# As another proxy of the most active or laziest wild boar we took the net displacement here: net_displacent

ws_newyear_net_displacement <- ws_newyear %>%
  mutate(
    net_displacement = sqrt((E-lead(E, 20))^2+(N-lead(N, 20))^2)
  )

```


In this case to decided to derive the mean speed and mean displacement in one day intervals 

1. We roundet the date by days
2. We grouped by TierName and datetime_round
3. We derived the mean speed and displacement

in this case without the geometry because of the reduced computational effort
```{r message = FALSE, warning=FALSE}

ws_newyear_speed %>%
  st_drop_geometry() %>%
  mutate(datetime_round = lubridate::round_date(as.POSIXct(DatetimeUTC),unit = "1 day")) %>%
  group_by(TierName, datetime_round) %>%
  summarise(speed_mean = mean(speed)) -> ws_newyear_speed_mean


ws_newyear_steplength %>%
  st_drop_geometry() %>%
  mutate(datetime_round = lubridate::round_date(as.POSIXct(DatetimeUTC),unit = "1 day")) %>%
  group_by(TierName, datetime_round) %>%
  summarise(steplength_mean = mean(steplength)) -> ws_newyear_steplength_mean


ws_newyear_net_displacement %>%
  st_drop_geometry() %>%
  mutate(datetime_round = lubridate::round_date(as.POSIXct(DatetimeUTC),unit = "1 day")) %>%
  group_by(TierName, datetime_round) %>%
  summarise(net_displacement = mean(net_displacement)) -> ws_newyear_net_displacement

```


### Moving window approach

The Moving window approach in order to reduce noise of the data might be another approach to analyse i.e. speed_mean but was not further been elaborated in this project. The idea is to sum up in this case six and five mean variables like speed_mean to smooth out  movement peeks over the given timeperiod. This allows to visualize the movement patterns in a more trend driven way.
```{r message = FALSE, warning = FALSE, results='hide', fig.show = TRUE}

# Here we can see the overall movements of the seven wild boar in a smooth out way (derived by the rollmean function) and the original speedmean.

ws_newyear_speed_mean %>% 
  head(100) %>%
  mutate(rollmean = zoo::rollmean(speed_mean, 6, fill = NA, align = "center")) %>%
  ggplot(aes(datetime_round)) +
  geom_line(aes(y = speed_mean, colour = "speedmean")) +
  #geom_point(aes(y = speed_mean)) +
  geom_line(aes(y = rollmean, colour = "rollmean")) 

# An idea would have been to derive the rollmean of the individuals and compare them among each other.
# i.e.:
ws_newyear_speed_mean %>% 
  head(37) %>%
  mutate(rollmean = zoo::rollmean(speed_mean, 5, fill = NA, align = "center")) %>%
  ggplot(aes(datetime_round)) +
  geom_line(aes(y = rollmean, colour = "TierName"))

```



### Visualization of activity patterns 

First:      Calculating Mean Steplengh
, Second:     Plotting with geom_tile 
, Y =         TierName
, X =         mean hours of the day
, fill =      steplegth


Core result of the question answered: which is the most active / laziest wildboar. The interpretation is still a vage idea of what "active" / "laziest" means but in thsi project we defined it as the most active wildboar over a certain timeperiod. The results show clear "winners" and "loosers" when having a look on the mean_speed and mean_net_displacement over the evaluated timeperiod. We interpreted the results in the way that in our point of view the wildboar with the highest steplength, speed or netto displacement got evaluated as the most active wildboar and vice versa. In order to backup that we also derived the overall mean speed and netdisplacement of the individuals in order back up our hypothesis.
```{r message = FALSE, warning=FALSE}

# steplength_mean

ws_newyear_steplength_mean %>%
count(datetime_round, TierName) %>%
ggplot(mapping = aes(x = datetime_round, y = TierName)) +
geom_tile(mapping = aes(fill = ws_newyear_steplength_mean$steplength_mean)) 


# speed_mean

ws_newyear_speed_mean %>%
count(datetime_round, TierName) %>%
ggplot(mapping = aes(x = datetime_round, y = TierName)) +
geom_tile(mapping = aes(fill = ws_newyear_speed_mean$speed_mean)) 

view(ws_newyear_speed_mean)


#net displacement

ws_newyear_net_displacement %>%
count(datetime_round, TierName) %>%
ggplot(mapping = aes(x = datetime_round, y = TierName)) +
geom_tile(mapping = aes(fill = ws_newyear_net_displacement$net_displacement)) 

view(ws_newyear_net_displacement)

``` 



Different visualization approaches  might be even more useful in order to derive the real overall "laziness" or "activeness"


```{r message = FALSE, warning = FALSE, results='hide', fig.show = TRUE}
# i.e. the geom_point to derive the most active or laziest wildboar
ggplot(data = ws_newyear_steplength_mean, aes(datetime_round, steplength_mean, colour=TierName)) + geom_point()


# An alternative of the geom_tile visualization approach which basically does not show anything new.
# A more interesting visualization approach seems to be the use of the geom_boxplot:
  

ggplot(data = ws_newyear_speed_mean, aes(x=TierName, y = speed_mean)) +
geom_boxplot()


ggplot(data = ws_newyear_steplength_mean, aes(x=TierName, y = steplength_mean)) +
geom_boxplot()


ggplot(data = ws_newyear_net_displacement, aes(x=TierName, y = net_displacement)) +
geom_boxplot()

# These boxplots show the overall mean proxies of our indicator like speed /  steplength and net displacement of the individuals and are therefore are clearly the most adequate ways to visualize the overall activeness.The overall winner therefore seems to be the individual Fritz whereas he has the highest mean speed, steplength and net displacement over the hole timeperiod chosen.The overall most laziest wildboar therefore seems to be the wildboar indivual Sabine.


# This can also be expressed in numbers:

ws_newyear_speed %>%
  group_by(TierName) %>%
  st_drop_geometry() %>%
  summarise(mean = mean(speed, na.rm =TRUE))

ws_newyear_steplength %>%
  group_by(TierName) %>%
  st_drop_geometry() %>%
  summarise(mean = mean(steplength, na.rm =TRUE))

# !
ws_newyear_net_displacement %>%
  group_by(TierName) %>%
  summarise(mean = mean(net_displacement, na.rm =TRUE))

# Interestingly the last lines of code show a different result whereas according to the overall mean of net displacement the winner seems to be the individual Caroline. We therefore correct our crowning and give the titel of the most adventurous wild boar = therefore most traveled wild boar to the indivual Caroline.

```

For this project we needed the following data: wild boar data are given by the course administration of Patterns & Trends in Environmental Data, ZHAW, orthoimages & maps are given by swisstopo (open access) and the spatial data are  given by geovite.ethz.ch (open access). An overview over the used data is given in table 1.

```{r message = FALSE, warning = FALSE}

library(knitr)

data_aquisistion <- data.frame(
  Data = c("Wild-Boar", "Orthophoto", "Map", "TLM_Landcover", "TLM_Streets", "TLM_Railway", "TLM_Building", "TLM_LeisureAreas"),
  Data_Format = c(".csv", ".tif", ".tif", ".geojson", ".geojson", ".geojson", ".geojson", ".geojson"),
  Geometry_Type = c("Points", "Raster", "Raster", "Polygon", "Lines", "Lines", "Polygon", "Polygon"),
  Projected_CRS = c("CH1903+ / LV95", "CH1903 / LV03", "CH1903 / LV03", "WGS 84", "CH1903 / LV03", "CH1903 / LV03", "CH1903 / LV03", "CH1903 / LV03")
)

kable(data_aquisistion, col.names = gsub("[_]", " ", names(data_aquisistion)), caption = "Table 1: Overwiev of the used data for this project")

```

After loading the necessary libraries and the data acquisition in R (version 4.2.1), we converted their different coordinate reference system into a consistent one (CH1903+ / LV95). Then, the data are clipped to the study area with the extension of 2'567000/1'202000 to 2'573000/1'207000 with the function `st_intersection()`. The study area is located in the canton of Bern, district Seeland, Commune Gempelen and is located near the lake Neuchâtel. To reduce the amount of data volume - due to hardware limitation - only 7 of 19 wild boars were taken and the time period from 15.12.2014 until the 15.01.2015 was chosen. The result therefore is rather a simplified way to solve our question but includes all the necessary data to answer our research questions.

```{r message = FALSE, warning = FALSE , results = FALSE, fig.show = 'hide'}



### Data Import:

Wildschwein_sf <- st_as_sf(wildschwein_BE,                            # Convert wild-boar csv-data in Spatial Object
                              coords = c("E", "N"), 
                              crs = 2056)
Study_Area <- st_read("StudyArea.geojson")                            # Import Study Area
Orthophoto <- rast("Swissimage_1m_2014.tif")                          # Import Orthophoto as Raster-Data
Map <- terra::rast("Map_1to25000_2018.tif")                                  # Import Map as Raster-Data
Feldfruechte <- st_read("Feldfruechte_1m_2021.geojson")
TLM_Bodenbedeckung <- st_read("TLM_Bodenbedeckung_2020.geojson")      # Import Landcover-Types
TLM_Strassen <- st_read("TLM_Strassen_2020.geojson")                  # Import Roads
TLM_Eisenbahn <- st_read("TLM_Eisenbahn_2020.geojson")                # Import Railway-Lines
TLM_Gebaeude <- st_read("TLM_Gebaeude_Foodprint_2020.geojson")        # Import Buildings
TLM_Freizeitareale <- st_read("TLM_Freizeitareale_2020.geojson")      # Import Leisure-Areas


### Convert CRS:

Wildschwein_sf          # Projected CRS: CH1903+ / LV95
Study_Area              # Projected CRS: CH1903+ / LV95
Orthophoto              # Projected CRS: CH1903 / LV03
Map                     # Projected CRS: CH1903 / LV03
Feldfruechte            # Projected CRS: CH1903+ / LV95
TLM_Bodenbedeckung      # Projected CRS: WGS 84
TLM_Strassen            # Projected CRS: CH1903 / LV03
TLM_Eisenbahn           # Projected CRS: CH1903 / LV03
TLM_Gebaeude            # Projected CRS: CH1903 / LV03
TLM_Freizeitareale      # Projected CRS: CH1903 / LV03

TLM_Bodenbedeckung <- st_transform(TLM_Bodenbedeckung, crs = st_crs(2056))
TLM_Strassen <- st_transform(TLM_Strassen, crs = st_crs(2056))
TLM_Eisenbahn <- st_transform(TLM_Eisenbahn, crs = st_crs(2056))
TLM_Gebaeude <- st_transform(TLM_Gebaeude, crs = st_crs(2056))
TLM_Freizeitareale <- st_transform(TLM_Freizeitareale, crs = st_crs(2056))
Study_Area_for_Raster <- st_transform(Study_Area, crs = st_crs(21781))


### Objektart as Numeric:

TLM_Bodenbedeckung$objektart <- as.numeric(TLM_Bodenbedeckung$objektart)
TLM_Strassen$objektart <- as.numeric(TLM_Strassen$objektart)
TLM_Eisenbahn$objektart <- as.numeric(TLM_Eisenbahn$objektart)
TLM_Gebaeude$objektart <- as.numeric(TLM_Gebaeude$objektart)
TLM_Freizeitareale$objektart <- as.numeric(TLM_Freizeitareale$objektart)


### Downsizing Orthophoto

Orthophoto <- aggregate(Orthophoto, fact=2)

### Clip Data to Study_Area

Wildschwein_sf <- st_intersection(Wildschwein_sf, Study_Area)
Orthophoto <- crop(x = Orthophoto, y = Study_Area_for_Raster)
Feldfruechte <- st_intersection(Feldfruechte, Study_Area)
TLM_Bodenbedeckung <- st_intersection(TLM_Bodenbedeckung, Study_Area)
TLM_Strassen <- st_intersection(Study_Area, TLM_Strassen)
TLM_Eisenbahn <- st_intersection(Study_Area, TLM_Eisenbahn)
TLM_Gebaeude <- st_intersection(Study_Area, TLM_Gebaeude)
TLM_Freizeitareale <- st_intersection(Study_Area, TLM_Freizeitareale)


### Choose Wild-Boar Data from 2014 to 2015

Wildschwein_select <- Wildschwein_sf %>% 
  filter(DatetimeUTC >= as.Date("2014-12-15") & DatetimeUTC < as.Date("2015-01-15"))

timespan <- as.numeric(difftime(time1 = "2015-01-15", time2 = "2014-12-15", units = "secs"))


### Add Metadata
### Bodenbedeckung:

objektart <- c(1:15)
objektart_Beschreibung <- c("Fels", "Fels locker", "Felsbloecke", "Felsbloecke locker", "Fliessgewaesser", "Gebueschwald", "Lockergestein", "Lockergestein locker", "Gletscher", "Stehende Gewaesser", "Feuchtgebiet", "Wald", "Wald offen", "Gehoelzflaeche", "Schneefeld Toteis")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Bodenbedeckung <-left_join(TLM_Bodenbedeckung, Attributnamen, by = "objektart")


### Strassen:

objektart <- c(1:23)
objektart_Beschreibung <- c("Ausfahrt", "Einfahrt", "Autobahn", "Raststaette", "Verbindung", "Zufahrt", "Dienstzufahrt", "10m Strasse", "6m Strasse", "4m Strasse", "3m Strasse", "Platz", "Autozug", "Faehre", "2m Weg", "1m Weg", "1m Wegfragment", "2m Wegfragment", "Markierte Spur","8m Strasse","Autostrasse","Klettersteig", "Provisorium")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Strassen <-left_join(TLM_Strassen, Attributnamen, by = "objektart")


### Eisenbahn:

objektart <- c(0,2,4,5)
objektart_Beschreibung <- c("Normalspur", "Schmalspur", "Schmalspur mit Normalspur", "Kleinbahn")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Eisenbahn <-left_join(TLM_Eisenbahn, Attributnamen, by = "objektart")


### Gebaeude:

objektart <- c(0:22)
objektart_Beschreibung <- c("Gebaeude", "NA", "Hochhaus", "Hochkamin", "Turm", "Kuehlturm", "Lagertank", "Lueftungsschacht", "Offenes Gebaeude", "Treibhaus", "Im Bau", "Kapelle", "Sakraler Turm", "Sakrales Gebaeude", "NA", "Flugdach", "Unterirdisches Gebaeude", "Mauer gross", "Mauer gross gedeckt", "Historische Baute", "NA", "NA", "Verbindungsbruecke")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Gebaeude <-left_join(TLM_Gebaeude, Attributnamen, by = "objektart")


### Freizeitareale:

objektart <- c(0:7)
objektart_Beschreibung <- c("Campingplatzareal", "Freizeitanlagenareal", "Golfplatzareal", "Pferderennbahnareal", "Schwimmbadareal", "Sportplatzareal", "Standplatzareal", "Zooareal")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Freizeitareale <-left_join(TLM_Freizeitareale, Attributnamen, by = "objektart")

```

### The most fearful and the most brave wild boar

To describe the effect of the human influence areas at the activity-patterns of the wild boars, the question was asked: What is the most fearful and the most brave wild boar? The "fearful" wild boar is defined as the animal which avoids urban areas. The "brave" wild boar is the one that ventures closest to settlements. The ranking was based on the time spent in human influence areas as a percentage over the entire study period (31 days). 

To define the human influence areas - such as streets, railway, building and leisure areas - the data sets were first combined by `union()`. Then a buffer zone of 100 m was created around the human influence areas (`buffer()`). This range corresponds to the escape distance of 100 m to 200 m of wild boars given in the literature (Suter et al., 2018; Thurfjell et al. 2013). After joining the wild boar data with the Human Influence Areas Buffers (`st_join()`), the time difference between subsequent rows was calculated with `difftime()`. All categories of the urban areas were combined and named "Human Influence Areas" and all natural environment as "Nature". In Figure 1 a) are all human influence areas in the study area shown and in b) the 100 m buffer zone around the human influence areas.

```{r message = FALSE, warning = FALSE, results='hide', fig.show = TRUE}

### Combine Human Influence Areas.
### Geometry Type: Lines

Strassen_kl <- TLM_Strassen[,c("objektart_Beschreibung", "geometry")]
Eisenbahn_kl <- TLM_Eisenbahn[,c("objektart_Beschreibung", "geometry")]

Lines <- union(Strassen_kl, Eisenbahn_kl)
Lines <- st_as_sf(Lines)


### Geometry Type: Polygons

Gebaeude_kl <- TLM_Gebaeude[,c("objektart_Beschreibung", "geometry")]
Freizeitareale_kl <- TLM_Freizeitareale[,c("objektart_Beschreibung", "geometry")]

Polygons <- union(Gebaeude_kl, Freizeitareale_kl)
Polygons <- st_as_sf(Polygons)


### Total Human Influence Areas.

Human_Influence_Areas <- union(Lines, Polygons)
Human_Influence_Areas <- st_as_sf(Human_Influence_Areas)


### Create Buffer around Human Influence Areas.

Human_Influence_Areas_Buffer <- st_buffer(x = Human_Influence_Areas, dist = 100)


### Plot Human Influence Areas

Human_Influence_Areas_Plot <- tm_shape(shp = Orthophoto) +
    tm_rgb() +
  tm_shape(shp = Wildschwein_select) + 
    tm_dots(col = "TierName") +
  tm_shape(shp = Human_Influence_Areas) + 
    tm_polygons(col = "objektart_Beschreibung") +
    tm_lines(col = "objektart_Beschreibung") +
  tm_compass(type = "arrow", position = c(0.247,0.028), bg.color = "white", bg.alpha = 0.75, size = 1.8) + 
  tm_scale_bar(breaks = c(0, 0.25, 0.5, 0.75 ,1), text.size = 0.75, position = c("left", "bottom"), bg.color = "white", bg.alpha = 0.75) +
  tm_layout(main.title = "a)",
            main.title.size = 1,
            legend.title.size = 1,
            legend.title.color = "white",
            legend.text.size = 0.6,
            legend.outside = TRUE,
            legend.bg.color = "white",
            legend.bg.alpha = 1)

Human_Influence_Areas_Buffer <- mutate(Human_Influence_Areas_Buffer,Human_Influence_Areas =  "Human Influence Areas")
  
Human_Influence_Areas_Buffer_Plot <- tm_shape(shp = Orthophoto) +
    tm_rgb() +
  tm_shape(shp = Human_Influence_Areas_Buffer) + 
    tm_polygons(col = "Human_Influence_Areas", palette = "grey") +
  tm_shape(shp = Wildschwein_select) +
    tm_dots(col = "TierName") +
    tm_compass(type = "arrow", position = c(0.247,0.028), bg.color = "white", bg.alpha = 0.75, size = 1.8) + 
  tm_scale_bar(breaks = c(0, 0.25, 0.5, 0.75 ,1), text.size = 0.75, position = c("left", "bottom"), bg.color = "white", bg.alpha = 0.75) +
  tm_layout(main.title = "b)",
            main.title.size = 1,
            legend.title.size = 1,
            legend.title.color = "white",
            legend.text.size = 0.6,
            legend.outside = TRUE,
            legend.bg.color = "white",
            legend.bg.alpha = 1)


### most fearful/brave wild boar

Wildboar_brave <- st_join(x = Wildschwein_select, y = Human_Influence_Areas_Buffer)

Wildboar_brave$objektart_Beschreibung <- replace_na(data = Wildboar_brave$objektart_Beschreibung, replace = "Wald&Wiesen&Natur")

Wildboar_brave <- mutate(Wildboar_brave, Human_Influence_Areas = if_else(objektart_Beschreibung == "Wald&Wiesen&Natur", "Nature", "Human_Influence_Areas"))

Wildboar_brave <- st_drop_geometry(Wildboar_brave)

Wildboar_brave <- mutate(Wildboar_brave,time_of_stay = as.integer(difftime(time1 = lead(DatetimeUTC), time2 = DatetimeUTC), units = "secs"))

Wildboar_brave <- Wildboar_brave[,c("TierName", "objektart_Beschreibung", "time_of_stay", "Human_Influence_Areas")]

Wildboar_brave_list <-  Wildboar_brave %>%
  filter(time_of_stay >0) %>%
  group_by(TierName, Human_Influence_Areas) %>%
  summarise(time_of_stay_s = sum(time_of_stay)) %>%
  mutate(time_of_stay_percent = (time_of_stay_s/timespan)*100)

```

```{r message = FALSE, warning = FALSE, results='hide', fig.show = TRUE, fig.cap = "Figure 1: a) all human influence areas in the study area; b) the 100 m buffer zone around the human influence areas."}

Human_Influence_Areas_Plot
Human_Influence_Areas_Buffer_Plot

```

### Where wild boars stay

xxx


## Results

### The most fearful and the most brave wild boar

The effect of the human influence areas at the activity-patterns of the wild boars is shown in Figure 2. The duration of stay in urban areas is different for each animal. It is clearly seen, that the wild boars "Sabine" and "Ruth" venture closest to settlements. Whereas "Isabelle" and "Rosa" avoid the human influence areas and and prefer to stay in nature. The exact values and the ranking for each wild boar are given in table 2 & 3.

```{r message = FALSE, warning = FALSE, results='hide', fig.show = TRUE, fig.cap = "Figure 2: Time stay in human influence areas and nature as a percentage over the entire study period (31 days) of the seven wild boars."}

# Plot
Wildboar_brave_list_plot <- ggplot(Wildboar_brave_list, aes(x = TierName, y = time_of_stay_percent, fill = Human_Influence_Areas)) +
  geom_col() +
  theme_classic() +
  labs(y = "Duration of Stay [%]", x = "Wild Boar Name") +
  guides(fill=guide_legend(title="Land Type")) +
  scale_fill_manual(values = c("grey", "darkolivegreen3"))
Wildboar_brave_list_plot

```

```{r message = FALSE, warning = FALSE}
# Ranking brave
Wildboar_brave_rank <- Wildboar_brave_list %>%
  group_by(TierName) %>%
  filter(Human_Influence_Areas == "Human_Influence_Areas") %>%
  arrange(desc(time_of_stay_percent))
Wildboar_brave_rank$Rank <- 1:nrow(Wildboar_brave_rank)
Wildboar_brave_rank$Tier_Name <- Wildboar_brave_rank$TierName
Wildboar_brave_rank$Duration_of_Stay <- Wildboar_brave_rank$time_of_stay_percent
Wildboar_brave_rank <- Wildboar_brave_rank[,c("Tier_Name", "Duration_of_Stay", "Rank")]
Wildboar_brave_rank$Duration_of_Stay <- round(Wildboar_brave_rank$Duration_of_Stay, digits = 0)

kable(Wildboar_brave_rank, col.names = gsub("[_]", " ", names(Wildboar_brave_rank)), caption = "Table 2: The exact values and the ranking for the brave wild boar (Duration of Stay in Percent)")


# Ranking fearful
Wildboar_fearful_rank <- Wildboar_brave_list %>%
  group_by(TierName) %>%
  filter(Human_Influence_Areas == "Nature") %>%
  arrange(desc(time_of_stay_percent))
Wildboar_fearful_rank$Rank <- 1:nrow(Wildboar_fearful_rank)
Wildboar_fearful_rank$Tier_Name <- Wildboar_fearful_rank$TierName
Wildboar_fearful_rank$Duration_of_Stay <- Wildboar_fearful_rank$time_of_stay_percent
Wildboar_fearful_rank <- Wildboar_fearful_rank[,c("Tier_Name", "Duration_of_Stay", "Rank")]
Wildboar_fearful_rank$Duration_of_Stay <- round(Wildboar_fearful_rank$Duration_of_Stay, digits = 0)

kable(Wildboar_fearful_rank, col.names = gsub("[_]", " ", names(Wildboar_fearful_rank)), caption = "Table 2: The exact values and the ranking for the fearful wild boar (Duration of Stay in Percent)")

```

### Where wild boars stay

xxx


## Discussion

- present the results of your study and discuss them in the light of your research questions. What
have you achieved and what would be further steps for future research?
- report problems and limitations you encountered along the way and the solutions you chose to
overcome these, be it limitations with respect to the data sources, the tools or any other source of
limitation.
- discuss your data science choices in the light of the theory covered in the lectures, group works,
and your reading assignments.


## Bibliography

M. Noelia Barrios-Garcia, Sebastian A. Ballari, "Impact of wild boar (Sus scrofa) in its introduced and native range: a review", Biol Invasions, vol, 14, pp. 2283–2300, 2012,  https://link.springer.com/content/pdf/10.1007/s10530-012-0229-6.pdf.

X. J. Meng, D. S. Lindsay, and N. Sriranganathan, "Wild boars as sources for infectious diseases in livestock and humans", Philosophical Transactions of the Royal Society B: Biological Sciences, vol. 364, no. 1530, pp. 2697–2707, 2009,  https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2865094/pdf/rstb20090086.pdf.

Anneleen Rutten, Jim Casaer, Diederik Strubbe and Herwig Leirs, "Agricultural and landscape factors related to increasing wild boar agricultural damage in a highly anthropogenic landscape", Wildlife Biology, vol. 2020, no. 1, pp. 1-11, 2020, https://onlinelibrary.wiley.com/doi/pdf/10.2981/wlb.00634.

Henrik Thurfjell, Göran Spong & Göran Ericsson, "Effects of hunting on wild boar Sus scrofa behaviour", Wildlife Biology, vol. 2020, no. 19, pp. 87-93, 2020, https://bioone.org/journals/wildlife-biology/volume-19/issue-1/12-027/Effects-of-hunting-on-wild-boar-Sus-scrofa-behaviour/10.2981/12-027.pdf.

Suter Stefan, Sandro Stoller & Benjamin Sigrist, "Prävention von Wildschweinschäden in der Landwirtschaft und Management von Wildschweinen in Schutzgebieten", Schlussbericht, 2018, https://www.zhaw.ch/storage/hochschule/medien/bildmaterial/Schlussbericht_Wildschweinschreck.pdf.

