
---
title: "Spatial Analyses of wild boars data regarding on psycological patterns"
subtitle: "Semester Project for Patterns & Trends in Environmental Data FS22"
author: "Authors: Jonas Michael Windisch and Johannes Quente"
date: "Submission Date: 03.07.2022"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    code_download: true
    output_dir: "docs"
    code_folding: show
---

<style>
body {
text-align: justify}
</style>


## Abstract

xxx


## Introduction


In recent decades, an expansion and increase of wild boar (*Sus scrofa*) populations has been observed across Europe, with colonising agricultural and urban areas, thus increasing problems of cohabitation with humans (Rutten et al., 2020). In particular, the wild boar often comes into conflict with humans, the main problems being the transmission of diseases to domestic animals and humans, collisions with vehicles, disturbance or threat to citizens and damage to gardens, public parks, pasture and agriculture (Meng et al. 2009).

Wild boar damage to croplands is expressed in different ways: direct consumption of crops, rooting in search of bulbs, invertebrates or tubers, seed removal, trampling and damage to agricultural infrastructure (Barrios-García & Ballari 2012). Therefore, it is important to know their activity patterns and where and when the wild boars are in order to take countermeasures.

The research question been asked is: How can the different environments (settlements, streets and different land use categories) been contextualized with the activity-patterns of the wild boar-data. How can this be conceptualized, modeled and further implemented in suitable visualizations to show behavioral patterns given to a certain environmental context and help to answer questions like “What does wild boar fear?” or “What are the behavioral constraints of wild boars?”.


## Material and Methods

For this project we needed the following data: wild boar data are given by the course administration of Patterns & Trends in Environmental Data, ZHAW, orthoimages & map are given by swisstopo (open access) and the spatial data are  given by geovite.ethz.ch (open access). An overview over the used data is given in tabel 1.

```{r}

library(knitr)

data_aquisistion <- data.frame(
  Data = c("Wild-Boar", "Orthophoto", "Map", "TLM_Landcover", "TLM_Streets", "TLM_Railway", "TLM_Building", "TLM_LeisureAreas"),
  Data_Format = c(".csv", ".tif", ".tif", ".geojson", ".geojson", ".geojson", ".geojson", ".geojson"),
  Geometry_Type = c("Points", "Raster", "Raster", "Polygon", "Lines", "Lines", "Polygon", "Polygon"),
  Projected_CRS = c("CH1903+ / LV95", "CH1903 / LV03", "CH1903 / LV03", "WGS 84", "CH1903 / LV03", "CH1903 / LV03", "CH1903 / LV03", "CH1903 / LV03")
)

kable(data_aquisistion, col.names = gsub("[_]", " ", names(data_aquisistion)), caption = "Table 1: Overwiev of the used data for this project")

```

After loading the necessary libraries and the data acquisition, we converted their different coordinate reference system into a consistent one (CH1903+ / LV95). Then, the data are clipped to the study area with the extension of 2567000/1202000 to 2573000/1207000. The study area is located in the canton of Bern, district Seeland, Commune Gempelen and lies directly on lake Neuchâtel. To reduce the amount of data volume - due to hardware limitation - only 7 of 19 wild boars were taken and the time period from 2014-12-15 until the 2015-01-15 was chosen. The result therefore is rather a simplified way to solve our question but includes all the necessary data to answer our research questions.

```{r message = FALSE, warning = FALSE, echo = FALSE, eval = FALSE}

### Loading Libraries:

library(devtools)
library(ComputationalMovementAnalysisData)
library(ggplot2)
library(readr)
library(dplyr)
library(terra)
library(sf)
library(tmap)
library(SimilarityMeasures)
library(lubridate)
library(tidyr)
library(knitr)


### Data Import:

Wildschwein_sf <- st_as_sf(wildschwein_BE,                            # Convert wild-boar csv-data in Spatial Object
                              coords = c("E", "N"), 
                              crs = 2056)
Study_Area <- st_read("StudyArea.geojson")                            # Import Study Area
Orthophoto <- rast("Swissimage_1m_2014.tif")                          # Import Orthophoto as Raster-Data
Map <- terra::rast("Map_1to25000_2018.tif")                                  # Import Map as Raster-Data
Feldfruechte <- st_read("Feldfruechte_1m_2021.geojson")
TLM_Bodenbedeckung <- st_read("TLM_Bodenbedeckung_2020.geojson")      # Import Landcover-Types
TLM_Strassen <- st_read("TLM_Strassen_2020.geojson")                  # Import Roads
TLM_Eisenbahn <- st_read("TLM_Eisenbahn_2020.geojson")                # Import Railway-Lines
TLM_Gebaeude <- st_read("TLM_Gebaeude_Foodprint_2020.geojson")        # Import Buildings
TLM_Freizeitareale <- st_read("TLM_Freizeitareale_2020.geojson")      # Import Leisure-Areas


### Convert CRS:

Wildschwein_sf          # Projected CRS: CH1903+ / LV95
Study_Area              # Projected CRS: CH1903+ / LV95
Orthophoto              # Projected CRS: CH1903 / LV03
Map                     # Projected CRS: CH1903 / LV03
Feldfruechte            # Projected CRS: CH1903+ / LV95
TLM_Bodenbedeckung      # Projected CRS: WGS 84
TLM_Strassen            # Projected CRS: CH1903 / LV03
TLM_Eisenbahn           # Projected CRS: CH1903 / LV03
TLM_Gebaeude            # Projected CRS: CH1903 / LV03
TLM_Freizeitareale      # Projected CRS: CH1903 / LV03

TLM_Bodenbedeckung <- st_transform(TLM_Bodenbedeckung, crs = st_crs(2056))
TLM_Strassen <- st_transform(TLM_Strassen, crs = st_crs(2056))
TLM_Eisenbahn <- st_transform(TLM_Eisenbahn, crs = st_crs(2056))
TLM_Gebaeude <- st_transform(TLM_Gebaeude, crs = st_crs(2056))
TLM_Freizeitareale <- st_transform(TLM_Freizeitareale, crs = st_crs(2056))


### Objektart as Numeric:

TLM_Bodenbedeckung$objektart <- as.numeric(TLM_Bodenbedeckung$objektart)
TLM_Strassen$objektart <- as.numeric(TLM_Strassen$objektart)
TLM_Eisenbahn$objektart <- as.numeric(TLM_Eisenbahn$objektart)
TLM_Gebaeude$objektart <- as.numeric(TLM_Gebaeude$objektart)
TLM_Freizeitareale$objektart <- as.numeric(TLM_Freizeitareale$objektart)


### Clip Data to Study_Area

Wildschwein_sf <- st_intersection(Wildschwein_sf, Study_Area)
Feldfruechte <- st_intersection(Feldfruechte, Study_Area)
TLM_Bodenbedeckung <- st_intersection(TLM_Bodenbedeckung, Study_Area)
TLM_Strassen <- st_intersection(Study_Area, TLM_Strassen)
TLM_Eisenbahn <- st_intersection(Study_Area, TLM_Eisenbahn)
TLM_Gebaeude <- st_intersection(Study_Area, TLM_Gebaeude)
TLM_Freizeitareale <- st_intersection(Study_Area, TLM_Freizeitareale)


### Choose Wild-Boar Data from 2014 to 2015

Wildschwein_select <- Wildschwein_sf %>% 
  filter(DatetimeUTC >= as.Date("2014-12-15") & DatetimeUTC < as.Date("2015-01-15"))

timespan <- as.numeric(difftime(time1 = "2015-01-15", time2 = "2014-12-15", units = "secs"))

```

## Results

xxx


## Discussion

xxx


## Bibliography

M. Noelia Barrios-Garcia, Sebastian A. Ballari, "Impact of wild boar (Sus scrofa) in its introduced and native range: a review", Biol Invasions, vol, 14, pp. 2283–2300, 2012,             https://link.springer.com/content/pdf/10.1007/s10530-012-0229-6.pdf.

X. J. Meng, D. S. Lindsay, and N. Sriranganathan, "Wild boars as sources for infectious diseases in livestock and humans", Philosophical Transactions of the Royal Society B: Biological Sciences, vol. 364, no. 1530, pp. 2697–2707, 2009,             https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2865094/pdf/rstb20090086.pdf.

Anneleen Rutten, Jim Casaer, Diederik Strubbe and Herwig Leirs, "Agricultural and landscape factors     related to increasing wild boar agricultural damage in a highly anthropogenic landscape", Wildlife     Biology, vol. 2020, no. 1, pp. 1-11, 2020, https://onlinelibrary.wiley.com/doi/pdf/10.2981/wlb.00634.

