---
title: "Test-Area"
author: "Authors: Jonas Michael Windisch and Johannes Quente"
date: "Submission Date: 03.07.2022"
output: html_document
---


### Load the necessary Libraries.

```{r message = FALSE, warning=FALSE}

library(devtools)
library(ComputationalMovementAnalysisData)
library(ggplot2)
library(readr)
library(dplyr)
library(terra)
library(sf)
library(tmap)
library(SimilarityMeasures)
library(lubridate)
library(tidyr)

```


### Import the Data.

```{r message = FALSE, warning=FALSE}

Wildschwein_sf <- st_as_sf(wildschwein_BE,                            # Convert wild-boar csv-data in Spatial Object
                              coords = c("E", "N"), 
                              crs = 2056)
Study_Area <- st_read("StudyArea.geojson")                            # Import Study Area
Orthophoto <- rast("Swissimage_1m_2014.tif")                          # Import Orthophoto as Raster-Data
Map <- rast("Map_1to25000_2018.tif")                                  # Import Map as Raster-Data
Feldfruechte <- st_read("Feldfruechte_1m_2021.geojson")
TLM_Bodenbedeckung <- st_read("TLM_Bodenbedeckung_2020.geojson")      # Import Landcover-Types
TLM_Strassen <- st_read("TLM_Strassen_2020.geojson")                  # Import Roads
TLM_Eisenbahn <- st_read("TLM_Eisenbahn_2020.geojson")                # Import Railway-Lines
TLM_Gebaeude <- st_read("TLM_Gebaeude_Foodprint_2020.geojson")        # Import Buildings
TLM_Freizeitareale <- st_read("TLM_Freizeitareale_2020.geojson")      # Import Leisure-Areas

```


### Clean & Convert Data.

```{r message = FALSE, warning=FALSE}

### Convert CRS:

Wildschwein_sf          # Projected CRS: CH1903+ / LV95
Study_Area              # Projected CRS: CH1903+ / LV95
Orthophoto              # Projected CRS: CH1903 / LV03
Map                     # Projected CRS: CH1903 / LV03
Feldfruechte            # Projected CRS: CH1903+ / LV95
TLM_Bodenbedeckung      # Projected CRS: WGS 84
TLM_Strassen            # Projected CRS: CH1903 / LV03
TLM_Eisenbahn           # Projected CRS: CH1903 / LV03
TLM_Gebaeude            # Projected CRS: CH1903 / LV03
TLM_Freizeitareale      # Projected CRS: CH1903 / LV03

TLM_Bodenbedeckung <- st_transform(TLM_Bodenbedeckung, crs = st_crs(2056))
TLM_Strassen <- st_transform(TLM_Strassen, crs = st_crs(2056))
TLM_Eisenbahn <- st_transform(TLM_Eisenbahn, crs = st_crs(2056))
TLM_Gebaeude <- st_transform(TLM_Gebaeude, crs = st_crs(2056))
TLM_Freizeitareale <- st_transform(TLM_Freizeitareale, crs = st_crs(2056))


### Objektart as Numeric:

TLM_Bodenbedeckung$objektart <- as.numeric(TLM_Bodenbedeckung$objektart)
TLM_Strassen$objektart <- as.numeric(TLM_Strassen$objektart)
TLM_Eisenbahn$objektart <- as.numeric(TLM_Eisenbahn$objektart)
TLM_Gebaeude$objektart <- as.numeric(TLM_Gebaeude$objektart)
TLM_Freizeitareale$objektart <- as.numeric(TLM_Freizeitareale$objektart)


### Clip Data to Study_Area

Wildschwein_sf <- st_intersection(Wildschwein_sf, Study_Area)
TLM_Bodenbedeckung <- st_intersection(TLM_Bodenbedeckung, Study_Area)
TLM_Strassen <- st_intersection(Study_Area, TLM_Strassen)
TLM_Eisenbahn <- st_intersection(Study_Area, TLM_Eisenbahn)
TLM_Gebaeude <- st_intersection(Study_Area, TLM_Gebaeude)
TLM_Freizeitareale <- st_intersection(Study_Area, TLM_Freizeitareale)


### Choose Wild-Boar Data from 2014 to 2015

Wildschwein_select <- Wildschwein_sf %>% 
  filter(DatetimeUTC >= as.Date("2014-12-15") & DatetimeUTC < as.Date("2015-01-15"))

timespan <- as.numeric(difftime(time1 = "2015-01-15", time2 = "2014-12-15", units = "secs"))

```


### Add Metadata

```{r}
### Bodenbedeckung:

objektart <- c(1:15)
objektart_Beschreibung <- c("Fels", "Fels locker", "Felsbloecke", "Felsbloecke locker", "Fliessgewaesser", "Gebueschwald", "Lockergestein", "Lockergestein locker", "Gletscher", "Stehende Gewaesser", "Feuchtgebiet", "Wald", "Wald offen", "Gehoelzflaeche", "Schneefeld Toteis")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Bodenbedeckung <-left_join(TLM_Bodenbedeckung, Attributnamen, by = "objektart")


### Strassen:

objektart <- c(1:23)
objektart_Beschreibung <- c("Ausfahrt", "Einfahrt", "Autobahn", "Raststaette", "Verbindung", "Zufahrt", "Dienstzufahrt", "10m Strasse", "6m Strasse", "4m Strasse", "3m Strasse", "Platz", "Autozug", "Faehre", "2m Weg", "1m Weg", "1m Wegfragment", "2m Wegfragment", "Markierte Spur","8m Strasse","Autostrasse","Klettersteig", "Provisorium")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Strassen <-left_join(TLM_Strassen, Attributnamen, by = "objektart")


### Eisenbahn:

objektart <- c(0,2,4,5)
objektart_Beschreibung <- c("Normalspur", "Schmalspur", "Schmalspur mit Normalspur", "Kleinbahn")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Eisenbahn <-left_join(TLM_Eisenbahn, Attributnamen, by = "objektart")


### Gebaeude:

objektart <- c(0:22)
objektart_Beschreibung <- c("Gebaeude", "NA", "Hochhaus", "Hochkamin", "Turm", "Kuehlturm", "Lagertank", "Lueftungsschacht", "Offenes Gebaeude", "Treibhaus", "Im Bau", "Kapelle", "Sakraler Turm", "Sakrales Gebaeude", "NA", "Flugdach", "Unterirdisches Gebaeude", "Mauer gross", "Mauer gross gedeckt", "Historische Baute", "NA", "NA", "Verbindungsbruecke")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Gebaeude <-left_join(TLM_Gebaeude, Attributnamen, by = "objektart")


### Freizeitareale:

objektart <- c(0:7)
objektart_Beschreibung <- c("Campingplatzareal", "Freizeitanlagenareal", "Golfplatzareal", "Pferderennbahnareal", "Schwimmbadareal", "Sportplatzareal", "Standplatzareal", "Zooareal")
Attributnamen <- data.frame(objektart, objektart_Beschreibung)

TLM_Freizeitareale <-left_join(TLM_Freizeitareale, Attributnamen, by = "objektart")

```


### Overview Data.

```{r}

tm_shape(shp = Wildschwein_select) + 
  tm_dots(col = "TierName")

tm_shape(shp = TLM_Bodenbedeckung) + 
  tm_fill(col = "objektart_Beschreibung")

tm_shape(shp = TLM_Strassen) + 
  tm_lines(col = "objektart_Beschreibung")

tm_shape(shp = TLM_Eisenbahn) + 
  tm_lines(col = "objektart_Beschreibung")

tm_shape(shp = TLM_Gebaeude) + 
  tm_polygons(col = "objektart_Beschreibung")

tm_shape(shp = TLM_Freizeitareale) + 
  tm_polygons(col = "objektart_Beschreibung")

```


### Combine Human Influence Areas.

```{r}
### Geometry Type: Lines

Strassen_kl <- TLM_Strassen[,c("objektart_Beschreibung", "geometry")]
Eisenbahn_kl <- TLM_Eisenbahn[,c("objektart_Beschreibung", "geometry")]

Lines <- union(Strassen_kl, Eisenbahn_kl)
Lines <- st_as_sf(Lines)

tm_shape(shp = Lines) + 
  tm_lines(col = "objektart_Beschreibung")


### Geometry Type: Polygons

Gebaeude_kl <- TLM_Gebaeude[,c("objektart_Beschreibung", "geometry")]
Freizeitareale_kl <- TLM_Freizeitareale[,c("objektart_Beschreibung", "geometry")]

Polygons <- union(Gebaeude_kl, Freizeitareale_kl)
Polygons <- st_as_sf(Polygons)

tm_shape(shp = Polygons) + 
  tm_polygons(col = "objektart_Beschreibung")


### Total Human Influence Areas:

Human_Influence_Areas <- union(Lines, Polygons)
Human_Influence_Areas <- st_as_sf(Human_Influence_Areas)

tm_shape(shp = Human_Influence_Areas) + 
  tm_polygons(col = "objektart_Beschreibung")+
  tm_lines(col = "objektart_Beschreibung")

```



### Create Buffer around Human Influence Areas.

```{r}

Human_Influence_Areas_Buffer <- st_buffer(x = Human_Influence_Areas, dist = 25)

tm_shape(shp = Human_Influence_Areas_Buffer) + 
  tm_polygons(col = "grey") + 
  tm_shape(shp = Wildschwein_select) + 
    tm_dots(col = "TierName")

```



### Where the Wild-Boars stay I.

```{r}

Wildboar_brave <- st_join(x = Wildschwein_select, y = Human_Influence_Areas_Buffer)

Wildboar_brave$objektart_Beschreibung <- replace_na(data = Wildboar_brave$objektart_Beschreibung, replace = "Wald&Wiesen&Natur")

Wildboar_brave <- mutate(Wildboar_brave, Human_Influence_Areas = if_else(objektart_Beschreibung == "Wald&Wiesen&Natur", "Nature", "Human_Influence_Areas"))

Wildboar_brave <- st_drop_geometry(Wildboar_brave)

Wildboar_brave <- mutate(Wildboar_brave,time_of_stay = as.integer(difftime(time1 = lead(DatetimeUTC), time2 = DatetimeUTC), units = "secs"))

Wildboar_brave <- Wildboar_brave[,c("TierName", "objektart_Beschreibung", "time_of_stay", "Human_Influence_Areas")]

a <-  Wildboar_brave %>%
  filter(time_of_stay >0) %>%
  group_by(TierName, objektart_Beschreibung) %>%
  summarise(time_of_stay_s = sum(time_of_stay)) %>%
  mutate(time_of_stay_percent = (time_of_stay_s/timespan)*100)
a

ggplot(a, aes(x = TierName, y = time_of_stay_percent, fill = objektart_Beschreibung)) +
  geom_col()


b <-  Wildboar_brave %>%
  filter(time_of_stay >0) %>%
  group_by(TierName, Human_Influence_Areas) %>%
  summarise(time_of_stay_s = sum(time_of_stay)) %>%
  mutate(time_of_stay_percent = (time_of_stay_s/timespan)*100)
b

ggplot(b, aes(x = TierName, y = time_of_stay_percent, fill = Human_Influence_Areas)) +
  geom_col()

```



### The bravest/fearfulest Wild-Boar.

```{r}

### the bravest Wild-Boar

Wildboar_brave_rank <- b %>%
  group_by(TierName) %>%
  filter(Human_Influence_Areas == "Human_Influence_Areas") %>%
  arrange(desc(time_of_stay_percent))
Wildboar_brave_rank$Rank <- 1:nrow(Wildboar_brave_rank)

Wildboar_brave_rank


### the fearfulest Wild-Boar

Wildboar_fearful_rank <- b %>%
  group_by(TierName) %>%
  filter(Human_Influence_Areas == "Nature") %>%
  arrange(desc(time_of_stay_percent))
Wildboar_fearful_rank$Rank <- 1:nrow(Wildboar_fearful_rank)

Wildboar_fearful_rank

```



-----------------------------------------------------


### Create Agriculture Areas.

```{r}

Bodenbedeckung_kl <- TLM_Bodenbedeckung[,c("objektart_Beschreibung", "geometry")]

tm_shape(shp = Study_Area) + 
  tm_polygons(col = "green") +
  tm_shape(shp = Bodenbedeckung_kl) + 
    tm_polygons(col = "objektart_Beschreibung") +
  tm_shape(shp = Human_Influence_Areas) + 
    tm_polygons(col = "objektart_Beschreibung")





Not_Agriculture_Land <- union(Polygons, Bodenbedeckung_kl)
Not_Agriculture_Land <- st_as_sf(Not_Agriculture_Land)

tm_shape(shp = Study_Area) + 
  tm_polygons(col = "green")+
  tm_shape(shp = Not_Agriculture_Land) + 
    tm_polygons(col = "grey")


AgricultureLand <- st_difference(x = Study_Area, y = Not_Agriculture_Land)
  tm_shape(shp = AgricultureLand) + 
    tm_polygons(col = "grey")


ws_be_sf %>% 
  filter(DatetimeUTC >= as.Date("2014-12-15") & DatetimeUTC < as.Date("2015-01-15"))

```


-----------------------------------------------------


### Combine Nature/Aggriculture Land.

```{r}
Feldfruechte <- st_read("Feldfruechte_1m_2021.geojson")
TLM_Bodenbedeckung <- st_read("TLM_Bodenbedeckung_2020.geojson")
TLM_Bodenbedeckung <- st_transform(TLM_Bodenbedeckung, crs = st_crs(2056))
TLM_Bodenbedeckung$objektart <- as.numeric(TLM_Bodenbedeckung$objektart)
head(TLM_Bodenbedeckung)
head(Feldfruechte)

Bodenbedeckung_kl <- TLM_Bodenbedeckung[,c("objektart_Beschreibung", "geometry")]

Feldfruechte$objektart_Beschreibung <- Feldfruechte$Frucht
Feldfruechte$geometry <- Feldfruechte$geom
Feldfruechte_kl <- Feldfruechte[,c("objektart_Beschreibung", "geometry")]
v<-st_as_sfc(TLM_Bodenbedeckung)

Polygons<-union(Bodenbedeckung_kl, Feldfruechte_kl)
Polygons<-st_as_sf(Polygons)

tm_shape(shp = Polygons) + 
  tm_polygons(col = "objektart_Beschreibung")

st_sfc(Feldfruechte$geom)
Feldfruechte$geometry<-Feldfruechte$geom

rename_geometry <- function(g, name){
    current = attr(g, "sf_column")
    names(g)[names(g)==current] = name
    st_geometry(g)=name
    g
}
Feldfruechte<- rename_geometry(Feldfruechte, "geometry")

TLM_Bodenbedeckung<-st_cast(TLM_Bodenbedeckung, to = "POLYGON")

Feldfruechte<-st_zm(x = Feldfruechte, drop = F, what="Z")
TLM_Bodenbedeckung<-st_zm(x = TLM_Bodenbedeckung, drop = T)

tm_shape(shp = Feldfruechte) + 
  tm_polygons	(col = "Frucht") +tmap_options(max.categories = 44)+
tm_shape(shp = Wildschwein_sf) + 
    tm_dots(col = "TierName")

```



```{r}

tm_shape(shp = Wildschwein_sf) + 
    tm_dots(col = "TierName")

b<- tm_shape(shp = Orthophoto) + 
  tm_rgb() + 
  tm_shape(shp = Wildschwein_sf) + 
    tm_dots(col = "TierName") +
  tm_compass(type = "arrow", position = c(0.224,0.02), bg.color = "white", bg.alpha = 0.75, size = 1.8) + 
  tm_scale_bar(breaks = c(0, 0.5, 1, 1.5, 2), text.size = 0.75, position = c("left", "bottom"), bg.color = "white", bg.alpha = 0.75) +
  tm_credits("Scale: 1:25'000 \nData source: swisstopo, ZHAW \nAuthor: Windisch & Quente", fontface = "italic",  bg.color = "white", bg.alpha = 0.75, width = 1, position = c(0.72,0.02)) +
  tm_logo(file = "zhaw_lsfm_iunr_schwarz.png", position = c(0.78,0.86)) + 
  tm_layout(main.title = " Movement Patterns of Wild-Boar (Sus Scrofa) in the Seeland District (2014-2015)",
            main.title.size = 1,
            legend.title.size = 1,
            legend.text.size = 0.6,
            legend.position = c("left","top"),
            legend.bg.color = "white",
            legend.bg.alpha = 1,
            frame = F)

tmap_save(tm = b, filename = "b.pdf", width = 17, height = 14, units = "cm", dpi = 5000)

a<- tm_shape(shp = Map) + 
  tm_rgb()
tmap_save(tm = a, filename = "a.pdf", width = 17, height = 14, units = "cm", dpi = 5000)

tm_shape(shp = TLM_Gebaeude) + 
  tm_polygons	(col = "objektart")

```







```{r}

# Include tables with the function "kable"

knitr::kable(head(wildschwein_BE))
```

loading all Wildboar Data (n=4)
Sabi, Rosa, Ruth, Caro
```{r}


# loading .tif-dateien


#Beispieldaten <- terra::rast("Beispieldaten.tif")
#plot(Beispieldaten)
```


Adding background maps
```{r}

tmap_mode("view") +
tm_shape(pk100_BE) + 
  tm_rgb() +
  plot(Beispieldaten)
```

```{r}
ws_be <- read_csv("wildschwein_BE_2056.csv")

ws_be_sf <- st_as_sf(ws_be, coords = c("E", "N"), crs = 2056, remove = FALSE)


caro <- read_csv("caro60.csv")

```


joining caro + Sabi, Rosa, Ruth
```{r}

wildschweine(n=4) <- full_join(ws_be,caro,by = "gemeinsamkeit_bspw_Zeit")


```

Spliting wildboar data in wildboar individuals e.g.: Rosa and Sabi
```{r}
library(tidyverse)
ws %>% filter(TierName == "Sabi") -> ws_sabi2
ws %>% filter(TierName == "ruth") -> ws_ruth
ws %>% filter(TierName == "Rosa") -> ws_rosa
inner_join(ws_sabi, ws_rosa, by = "dt_rounded", suffix = c("_sabi", "_rosa")) %>% 
      mutate(distance = sqrt((E_sabi - E_rosa)^2 + (N_sabi - N_rosa)^2),
           meet = distance < 100) -> ws_join
```




--> How many individuals were tracked?
--> For which timesequence do we have comparable Data? 
--> average intervals? --> Making it comparable

  ```{r}
ws_be_sf %>% 
  st_drop_geometry() %>% 
  group_by(TierID, TierName) %>% 
  summarise(pings = n(),
            start_time = min(DatetimeUTC), 
            end_time = max(DatetimeUTC),
            avg_interval = mean(timelag, na.rm = T),
            total_tracking_time = sum(timelag, na.rm = T)) %>% 
  mutate(tracking_time_days = days(day(seconds_to_period(total_tracking_time)))) 


# average intervals
ws %>% 
  mutate(dt_rounded = round_date(DatetimeUTC, unit = "15 minutes")) -> ws 

```



Deriving movement parametern: Speed in meters per second

```{r}
ws_be_sf %>% 
  mutate(steplength = sqrt((E - lead(E,1))^2 + (N - lead(N,1))^2),
         speed = steplength/timelag)
```




## Specifying temporal windows
Our sampling interval is 1 minute - if we take a temporal window of 6 minutes we use a window size of 6 positions. Therefore that's 3 plus and 3 minus.
```{r}
caro %>% 
  mutate(
    nMinus3 = sqrt((lag(E,3)-E)^2 + (lag(N,3)-N)^2),
    nMinus2 = sqrt((lag(E,2)-E)^2+(lag(N,2)-N)^2),  
    nMinus1 = sqrt((lag(E,1)-E)^2+(lag(N,1)-N)^2),
    nPlus1  = sqrt((E-lead(E,1))^2+(N-lead(N,1))^2), 
    nPlus2  = sqrt((E-lead(E,2))^2+(N-lead(N,2))^2),  
    nPlus3  = sqrt((E-lead(E,3))^2+(N-lead(N,3))^2)  
) -> caro
caro %>% 
  rowwise() %>% 
  mutate(
    stepMean = mean(c(nMinus3, nMinus2, nMinus1, nPlus1, nPlus2, nPlus3))
  ) %>% 
  ungroup() -> caro
```


<!-- the following is just a placeholder text, remove it!-->
Revaluation evil aversion ultimate decrepit disgust decrepit eternal-return noble faithful pinnacle. Truth ascetic inexpedient decrepit free. Ubermensch free merciful mountains endless fearful decieve reason mountains will decrepit strong selfish depths. Overcome faith snare gains oneself transvaluation.




```{r}
# include plots automatically

ggplot(schreck_locations, aes(E, N)) +
  geom_point() +
  coord_map()

```



# Data exploration
```{r}
ws %>% 
  group_by("ruth") %>% 
  summarise(n = n())

summary("ruth")

str("ruth")

ggplot(ws) + geom_sf()
tm_shape(ws) + tm_dots(col = "ruth")

view(ws)

ggplot(caro) +
  geom_histogram(aes(stepMean), bins = 60) + geom_vline(xintercept = 4, color = "red")
summary(caro$stepMean)
``` 


# Visualisation of the spatio-temporal patterns
# Visualizing the percentage of samples in a given location
```{r}
ggplot(wildboar) +
  geom_polar(aes(rough_location))

#--> Excercise 5!!

``` 

# Visualization of activity patterns // maybe related to spatial context

```{r}
  wildboar %>%
    count(time, location) %>%
    ggplot(mapping = aes(x = time, y = location)) +
    geom_tile(mapping = aes(speed))
``` 
